Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-04 text/supp.tex
Integrate Trevor's comments and unwrap text

\item We removed all populations rated as $< 2$ in the GPDD quality assessment
  (on a scale of $1$ to $5$, with $1$ being the lowest quality data)
  \citep[following][]{sibly2005, ziebarth2010}

@@

\noindent
We provide a supplemental figure of all the time series included in our analysis
and indicate which values were interpolated (\percImputedPops\% of populations
had at least one point interpolated and only \percImputedPoints\% of the total
observations were interpolated) (Fig.~\ref{fig:all-ts}). Table S1 shows the
final taxonomic breakdown and the number of populations with interpolated
values.

>>>>

\item We removed all populations rated as $< 2$ in the GPDD quality assessment (on a scale of $1$ to $5$, with $1$ being the lowest quality data) \citep[following][]{sibly2005, ziebarth2010}.

@@

\noindent
We provide a supplemental figure of all the time series included in our analysis and indicate which values were interpolated (\percImputedPops\% of populations had at least one point interpolated also only \percImputedPoints\% of the total observations were interpolated) (Fig.~\ref{fig:all-ts}). Note that interpolation is highly unlikely to lead to black swan detections, since black swans involve extreme increases or decreases. Table S1 shows the final taxonomic breakdown and the number of populations with interpolated values.
